\chapter{Acknowledgements}    

I am grateful to several individuals who have assisted me during the course of this work. First, I would like to acknowledge my debt to my supervisor, Dr. Lo\"ic Markley, for introducing me to the world of electromagnetism, and micro-mentoring me throughout my graduate studies. His dead-on comments on my ideas and incisive responses to my many queries have critically facilitated my research. I consider myself to be only the first of many students who will grow through his admirable personality, white-hot brilliance, and intellectual guidance. My appreciation also goes to Dr. Kenneth Chau and Dr. Thomas Johnson, for seeing me through the whole course of this project. With their extensive expertise in the field of electromagnetics, they provided many new perspectives during my initial course works that later became instrumental for this work.

My tenure as a graduate student would not have been the same without the pointless corridor chats and laughs that I shared with my colleagues from the School of Engineering. A dept of gratitude is owed to my lab mates, Iman Ahganejad, Mohammed Al-Shakhs, Masoud Ahmadi and Max Bethune-Waddell, for their companionship during the pursuit of this goal. A warm word for my great friends Salamah Meherier, who has been a part of almost every episodes of my life in Kelowna, and Abhinav Karanam, with whom I had the best coffee breaks.
	
On a more personal note, I am forever grateful to my parents, Zakir and Airin, who have always been a major source of encouragment. I am proud to have your genes and look up to you more than anyone else. Thanks to my sister, Samira, for being my loyal `secret double agent' in the family. The villainous desire to start one more unnecessary argument with you kept me going for past two years. I am also indebted my aunts for keeping tabs on me from time to time. Especially, thanks to aunts Raina and Rebeka, for affording me two fabulous winter vacations. Last, but certainly not least, a special thank you to my fianc\'ee, Tabassum, for her good-humored friendship and covert support during the most stressful periods of this research. I look forward to our lifelong journey.